replication_report

### 2015-03-15 replication_report.Rmd
making a commit so that Yari can see this RMD
Layout of intentions for entire project timeline

Plan for replication project
(1) power analyses - with and without outliers
(2) moderation analysis by gender
(3) graph the results with ggplot2

1: Get data
```{r}
#load packages:
library(pwr)
library(dplyr)
library(plyr)
library(ggplot2)
library(MBESS)
library(psych)
library(car)
library(lsr)

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
head(dat)
View(dat)

>>>>

Plan for replication project
(1) Showing abbreviated version of the table 
(2) Explain what that table displays 
(3) R code to get there
----
Plan for added components for replication project (due later)
(1) power analyses - with and without excluded participants
(2) moderation analysis by gender
(3) graph the results with ggplot2

3: R code
```{r}
#load packages:
library(pwr)
library(dplyr)
library(plyr)
library(ggplot2)
library(MBESS)
library(psych)
library(car)
library(lsr)

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <- tbl_df(dat)
head(dat)
#View(dat)

??describe()
